Effects of the body force on the evacuation dynamics

### 2019-11-26 paper.tex
borre todo lo viejo y puse el grafico de te vs vd

\title{Effects of body force on the original Social Force Model}

@@

Pedestrian Dynamics \sep Social Force Model \sep 
Jamaraat Pilgrimage

@@

\section{\label{simulations}Setting and parameters}

\subsection{\label{software} Simulation software}

@@

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./vd_vs_te_ck.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./flow-density_vd1_multi_kn.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./histo_grado_density5_width22_kn0.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./histo_grado_density7_width22_kn0.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./histo_grado_density9_width22_kn0.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./histo_grado_density5_width22_knE5.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./histo_grado_density7_width22_knE5.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./histo_grado_density9_width22_knE5.eps}
\caption{\label{} }
\end{figure}

>>>>

\title{Effects of the body force on the evacuation dynamics}

@@

Pedestrian Dynamics \sep Social Force Model \sep Body Force

@@

\section{\label{simulations}Numerical simulations}

@@

\subsection{\label{bottleneck} Bottleneck}

@@

\subsection{\label{corridor} Corridor}

\subsection{\label{reduced-in-units} Reduced-in-units equation of motion}
